The Array of Long-Baseline Antennas for Taking Radio Observations from the Sub-Antarctic

### 2020-04-02 albatros_paper.tex
HCC a few more text edits

\subsection{Back-end electronics}
\textcolor{red}{\bf Nivek, HCC?} \\
The back end electronics consists of the bias tee, high pass filter
(HPF), low pass filter (LPF) and the Smart Network ADC Processor
(SNAP) board.  The signals are band limited to \SI{1.2}{MHz}-\SI{81}{MHz}.

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=0.7\linewidth]{Figures/autonomous.jpg}
    \caption{Single autonomous station pathfinder.  \textcolor{red}{\bf Add command module and electronics glamor shots.}}
    \label{Fig:autonomous}
  \end{center}
\end{figure}

\begin{figure}
  \begin{center}
    \includegraphics[width=\linewidth]{Figures/albatros_single_schematic/albatros_single_schematic.pdf}
    \caption{Schematic for the single autonomous station pathfinder.
      Data and RF connections are outlined in black, and power
      connections are outlined in red.  A dual-polarization LWA
      antenna, equipped with an active balun, is connected 50-m
      coaxial cables to the back-end readout electronics, which are
      housed in a Faraday cage denoted by the dashed box.  Each of the
      two antenna inputs is passed to a second-stage electronics chain
      consisting of a bias tee, high- and low-pass filters, and
      amplifier.  The signals are digitized at 250~Msamp/s by a SNAP
      board, and the on-board FPGA is programmed with firmware that
      computes averaged auto- and cross-spectra, as well as
      channelized baseband.  A Raspberry Pi controls the SNAP board
      and saves the data products to a combination of an SD card and
      external hard drives.  Timing information is provided by a
      GPS-discipined clock.  Power to the system is provided solar
      panels that charges a 24-V battery bank, which is regulated down
      to several other output levels.}
    \label{Fig:Signal Chain}
  \end{center}
\end{figure}

>>>>

\subsection{Back-end electronics}
\textcolor{red}{\bf Nivek, HCC?} \\

The back-end readout electronics are housed in a Faraday cage that is
located $\sim 100$~m away from the antennas to reduce potential
contamination from self-generated RFI.  Each of the four antenna
signals is passed to a second-stage electronics chain consisting of a
bias tee (Minicircuits ZFBT-4R2GW-FT+), amplifier (Minicircuits
ZX60-V63+), and a pair of high- and low-pass filters (Minicircuits
ZFHP-1R2+ and SLP-90+) that band limit the signal to
1.2--\SI{81}{MHz}.  A Smart Network ADC Processor (SNAP) board
digitizes the RF signals at 250~Msamp/s and calculates a full
cross-correlation of the four inputs, producing four auto- and six
cross-spectra as outputs.  \textcolor{red}{\bf finish merging text
  below into the above paragraph}

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=0.7\linewidth]{Figures/autonomous.jpg}
    \caption{Single autonomous station pathfinder installed at the
      hydro shack site.  The system is powered by a bank of solar
      panels that are visible in the background.  \textcolor{red}{\bf
        Add command module and electronics glamor shots.}}
    \label{Fig:autonomous}
  \end{center}
\end{figure}

\begin{figure}
  \begin{center}
    \includegraphics[width=\linewidth]{Figures/albatros_single_schematic/albatros_single_schematic.pdf}
    \caption{Schematic for the single autonomous station pathfinder.
      Data and RF connections are outlined in black, and power
      connections are outlined in red.  A dual-polarization LWA
      antenna, equipped with an active balun, is connected via 50-m
      coaxial cables to the back-end readout electronics, which are
      housed in a Faraday cage denoted by the dashed box.  Each of the
      two antenna inputs is passed to a second-stage electronics chain
      consisting of a bias tee, high- and low-pass filters, and
      amplifier.  The signals are digitized at 250~Msamp/s by a SNAP
      board, and the on-board FPGA is programmed with firmware that
      computes averaged auto- and cross-spectra, as well as
      channelized baseband.  A Raspberry Pi controls the SNAP board
      and saves the data products to a combination of an SD card and
      external hard drives.  Timing information is provided by a
      GPS-discipined clock.  Power to the system is provided solar
      panels that charges a 24-V battery bank, which is regulated down
      to several other output levels.}
    \label{Fig:Signal Chain}
  \end{center}
\end{figure}
